BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-03-30 manuscript/BarnebyLives An R package to create and qc herbarium labels.rmd
more data

# now copy bash script to location # note we are one dir up from the lowest level. 
p2libs <- system.file(package = 'BarnebyLives')
folds <- file.path( 'rmarkdown', 'render_labels.sh')

file.copy(from = file.path(p2libs, folds), 
          to = '/media/steppe/hdd/Barneby_Lives-dev/manuscript/labels/raw')
```

>>>>

# now copy bash script to location # note we are one dir up from the lowest level. 
# note that I customized the label template after import, so we will not run this again. 
# p2libs <- system.file(package = 'BarnebyLives')
# folds <- file.path( 'rmarkdown', 'render_labels.sh')

# file.copy(from = file.path(p2libs, folds), 
#           to = '/media/steppe/hdd/Barneby_Lives-dev/manuscript/labels/raw')
```

### 2025-03-30 manuscript/labels/skeleton.Rmd
more data

```{r load data}
data <- read.csv('../data/processed/cleaned_data.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_Uncertainty = '5m') |>
  dplyr::filter(Collection_number == params$Collection_number)
```

@@

`r writer(data$Habitat)`. `r data$physical_environ`  
Veg.: `r species_font(data$Vegetation)` `r associates_writer(data$Associates)`
`r writer(data$Notes)`  
\endgroup
\begingroup
\begin{spacing}{0.1}
{\scriptsize `r data$Directions_BL`}
\end{spacing}
\endgroup

>>>>

```{r load data}
data <- read.csv('../data/processed/cleaned_data.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_Uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number)
```

@@

`r writer(data$Habitat)`. `r data$physical_environ`  
Veg.: `r species_font(data$Vegetation)` `r associates_writer(data$Associates)`
`r writer(data$Notes)`  
\endgroup
